Applying Spatio-temporal Scan Statistics and Spatial Autocorrelation Statistics to identify Covid-19 clusters in the world.

### 2021-01-11 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 Considering the number of deaths per inhabitant, when identifying local spatial autocorrelation with the Local Moran's I  **(Picture 1)** after April, month with the highest Global Moran's I, spatial dependence was strong in Europe, South America and North America, with little difference in maps throughout the year. For the number of infections per inhabitant, after October, which was the first month with a high global dependence, local association was strong in Europe until the end of the year.

>>>>

 Considering the number of deaths per inhabitant, when identifying local spatial autocorrelation with the Local Moran's I  **(Picture 1)** after April, month with the highest Global Moran's I, spatial dependence was strong in Europe, South America and North America, with little difference in maps throughout the year. For the number of infections per inhabitant, after October, which was the first month with a high global dependence, local association was strong in Europe until the end of the year **(Picture 2)**.
